---
title: "Preliminary Results Report"
author: "Kosuke Sato"
date: "2023-10-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(patchwork)
pacman::p_load(tidyverse, gt, gtExtras, DT)
source("../code/main.R")
```

# Introduction
 My target paper is Mian et al. (2017). This paper investigates the relathionship between the household debt to GDP ration and GDP growth. 

# Preliminary Result
 The code is uploaded on my github repository. (https://github.com/1414satok/Mian-et-al-2017.git) I've almost finished to make table 1 and figure 1.   
 In table 1, I got almost the same results as the original paper by using the same data as it. But I have not calculated the serial correlation. It seems that this is calculated through redundant process, but I guess I can finish by the final presentation.

```{r}
gt(table1)
```

 The results of impulse response functions are almost same as the original ones, but it is not exactly. In original paper, they correct the bias of the response functions before the Cholesky decomposition. I have not understand why and how they do it. Besides, I have not yet finished estimating the confidence interval.
```{r}
g1 + g2 + g3
```

Henceforth, I am completing replication of the results in the section 3, and need to make 4 tables and 2 figures more.

# References
Atif Mian, Amir Sufi, Emil Verner, Household Debt and Business Cycles Worldwide, The Quarterly Journal of Economics, Volume 132, Issue 4, November 2017, Pages 1755–1817, https://doi.org/10.1093/qje/qjx017